Probability of causal contact between interstellar civilizations through MonteCarlo simulations

### 2019-08-16 manuscript.tex
waiting time...

In this section we analyze the distribution of the waiting times for
a first contact.
%
Such distribution can be considered to compute the probability of
reaching a first contact within the first XX years.

In the Fig.~\ref{F_waiting} we show the fraction of the CETIs that
have made at least one contact  as a funtion of the elapsed time since
the awakening, given that they make at least one contact on their
lifetime.
%
From a frequentist approach, the normalizaed cumulative counts are
related to the estimation of the probability of observing a given time
with no success.
%             
XX panels show the histograms of the waiting times for the first
contact, for all the CETIs that make at least one contact along their
lifetime.
%
We show separately the histograms for several values of $\tau_a$ and a
fixed value of $(\tau_s, D_{max})$, and for several values of $\tau_s$ and a
fixed value of $(\tau_a, D_{max})$.
%
For different values of $\tau_a$, the shape of the distribution is
similar, so that a normalization ... but not in the case of different values of $\tau_s$.

@@

   \caption{Fraction of the CETIs that have made at least one contact  
   as a funtion of the elapsed time since the awakening, given that
   they make at least one contact on their lifetime.
   %
   From a frequentist approach, this fraction is the estimation of the
   probability

   }
   \label{F_waiting}
\end{figure*}

\begin{figure*}
   \centering
   \includegraphics[width=0.33\textwidth]{prob1_10k.png}%
   \includegraphics[width=0.33\textwidth]{prob1_40k.png}%
   \includegraphics[width=0.33\textwidth]{prob1_80k.png}

   \caption{F_}
   \label{F_waiting}
\end{figure*}

>>>>

In this section we analyze the distribution of the waiting times for
a first contact.
%
Such distribution can be considered to compute the probability of
reaching a first contact within the first XX years of a SETI project,
assuming the methods are correct and the hypotheses of the experiment.

In the Fig.~\ref{F_waiting} we show the fraction of the CETIs that
have made at least one contact  as a funtion of the elapsed time since
the awakening, given that they make at least one contact on their
lifetime, for different models.
%
From a frequentist approach, the normalizaed cumulative counts are
related to the estimation of the probability of observing a given time
with no success.
%             
XX panels show the histograms of the waiting times for the first
contact, for all the CETIs that make at least one contact along their
lifetime.
%
We show separately the histograms for several values of $\tau_a$ and a
fixed value of $(\tau_s, D_{max})$, and for several values of $\tau_s$ and a
fixed value of $(\tau_a, D_{max})$.
%
For different values of $\tau_a$, the shape of the distribution is
similar, and the main difference given by the different number of
contacts on the different models.
%
Conversely, 
 For different values of $\tau_a$, the shape of the distribution is
similar, and the main difference given by the different number of
contacts on the different models.

... but not in the case of different values of $\tau_s$.

@@

   \caption{Fraction of the CETIs that have made at least one contact  
   as a funtion of the elapsed time since the awakening, given that
   they make at least one contact on their lifetime.
   %
   From a frequentist approach, this fraction is the estimation of the
   probability    
   }
   \label{F_waiting}
\end{figure*}

\begin{figure*}
   \centering
   \includegraphics[width=0.5\textwidth]{Figure_taua.png}%
   \includegraphics[width=0.5\textwidth]{Figure_taus.png}%
   %
   \caption{Histograms of the mean waiting times for the first contact, for
   several models.
   %
   Left panel shows the histograms for several values of $\tau_a$, and
   $\tau_s$ in the range 17000-24000 yr.
   %
   Right panel shows the histograms for several values of $\tau_s$, and
   $\tau_a$ in the range 68000-100000 yr.
   %
   The shape of the histograms does not change when $\tau_a$ is
   modified, but significantly changes when $\tau_s$ is modified.
   }
   \label{F_waiting}
\end{figure*}

\begin{figure*}
   \centering
   \includegraphics[width=0.33\textwidth]{prob1_10k.png}%
   \includegraphics[width=0.33\textwidth]{prob1_40k.png}%
   \includegraphics[width=0.33\textwidth]{prob1_80k.png}
   %
   \caption{F}
   \label{F_waiting}
\end{figure*}
